PANCHANGE_data_preprocessing

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
ocir prepand missigness added

## Missigness

## prepandemic
```{r PCL prepan missingness}
glad.pcl.raw.id <- glad.pcl.raw.id %>%
  mutate(
    na_per_person_pcl_prepan =         # variable for NA per person
      rowSums(                       
        is.na(.[pcl.items_prepan])
      )
  )

@@

# PHQ missingness (NAs per person)

## prepandemic
```{r PHQ prepan missingness}
glad.phq.raw.id <- glad.phq.raw.id %>%
  mutate(
    na_per_person_phq_prepan =         # variable for NA per person
      rowSums(                       
        is.na(.[phq.items_prepan])
      )
  )

@@

```{r PHQ prepan missingness 8 items}
glad.phq.raw.id <- glad.phq.raw.id %>%
  mutate(
    phq.missing_only_suicide_item_prepan = 
      if_else(
        condition = na_per_person_phq_prepan == 1 & 
          is.na(phq.dead_hurting_thoughts_prepan_numeric), 
        true = 1,
        false = 0,
        missing = NA_real_
      )
  )

@@

>>>>

prepandemic
```{r pcl prepan missingness}
glad.pcl.raw.id <- glad.pcl.raw.id %>%
  mutate(
    na_per_person_pcl_prepan =         # variable for NA per person
      rowSums(                       
        is.na(.[pcl.items_prepan])
      )
  )

@@

PHQ missingness (NAs per person)

prepandemic
```{r phq prepan missingness}
glad.phq.raw.id <- glad.phq.raw.id %>%
  mutate(
    na_per_person_phq_prepan =         # variable for NA per person
      rowSums(                       
        is.na(.[phq.items_prepan])
      )
  )

@@

```{r phq prepan missingness 8 items}
glad.phq.raw.id <- glad.phq.raw.id %>%
  mutate(
    phq.missing_only_suicide_item_prepan = 
      if_else(
        condition = na_per_person_phq_prepan == 1 & 
          is.na(phq.dead_hurting_thoughts_prepan_numeric), 
        true = 1,
        false = 0,
        missing = NA_real_
      )
  )

@@

prepandemic
```{r ocir prepan missingness}
glad.ocir.raw.id <- glad.ocir.raw.id %>%
  mutate(
    na_per_person_ocir_prepan =         # variable for NA per person
      rowSums(                       
        is.na(.[ocir.items_prepan])
      )
  )

glad.ocir.raw.id %>%
  freq(na_per_person_ocir_prepan,
       cumul = F)
```
